---
title: "Big Title"
author: "Author name"
institute: "Te Kāhui Roro Reo | New Zealand Institute of Language, Brain and Behaviour <br/> Te Whare Wānanga o Waitaha | University of Canterbury"
format:
  revealjs:
    theme: [custom.scss]
    incremental: true
    logo: images/NZILBB-small.svg
    title-slide-attributes:
      data-background-image: ../images/NZILBB-big.svg
      data-background-position: 'top left'
      data-background-size: 50%
    embed-resources: false
    include-in-header:
      - text: |
          <link rel="icon" type="image/png" sizes="32x32" href=".//images/fav.png" />
bibliography: 
  - grateful-refs.bib
editor: 
  markdown: 
    wrap: 72
execute: 
  echo: true
knitr:
  opts_chunk: 
    dev: "png"
    dev.args: 
      bg: "transparent"
---

```{r}
#| echo: false
# This is a place to load packages in the background (i.e., this block won't 
# apear on the slides because `echo` is false.)
library(tidyverse)
library(here)
```

# How to use me

## How to use me

- Most problems can be solved with the 
  [Quarto documentation](https://quarto.org/docs/presentations/).
- Some visual options are built into this template (in addition to those built in to Quarto). In the markdown use square
brackets around text you want to style and the style name in curly brakets. The
extra options are:

## Size 

<!-- If you want to see what these look like, you should render the document. -->
<!-- Click the 'render' button at the top of this pane (if using RStudio).
<!-- If you can't render the document, make sure you have installed any packages-->
<!-- mentioned in error messages -->

- `[example text]{.big}`: [example text]{.big}
- `[example text]{.real-big}`: [example text]{.real-big}
    
## Position

- Horizontal centring
- `[example text]{.centre}`

::: fragment
[example text]{.centre}
:::

## Colour

- `[example text]{.blue}`: [example text]{.blue}
- `[example text]{.red}`: [example text]{.red}

## 'Backlight'

- `backlight` produces a light shadow around text.
- Useful for text on top of background images.
- `[example text]{.backlight}`: [example text]{.backlight}
- `[example text]{.inverse-backlight}`: [example text]{.inverse-backlight}

## `grateful` and bibliographies

- This template includes `grateful`, which adds any R packages you use to your 
bibliography.
- To add references, follow the Quarto documentation. The simple story:
    - Add a `.bib` file to the directory containing your presentation with 
    all the things you want to cite.
    - Add the `.bib` file in the `bibliography` section of the frontmatter (i.e.
    in the list of options at the start of the `.qmd` file).
    - Include citations in markdown as normal, e.g. `[@bibentry]`

# References

```{r}
#| echo: false
grateful::nocite_references(
  grateful::cite_packages(output = "citekeys", out.dir = here())
)
```


::: refs

:::
