---
title: "Big Title"
author: "Author name"
institute: "Te Kāhui Roro Reo | New Zealand Institute of Language, Brain and Behaviour <br/> Te Whare Wānanga o Waitaha | University of Canterbury"
format:
  revealjs:
    theme: [custom.scss]
    incremental: true
    logo: images/NZILBB-small.svg
    title-slide-attributes:
      data-background-image: ../images/NZILBB-big.svg
      data-background-position: 'top left'
      data-background-size: 50%
    embed-resources: false
    include-in-header:
      - text: |
          <link rel="icon" type="image/png" sizes="32x32" href=".//images/fav.png" />
bibliography: 
  - grateful-refs.bib
editor: 
  markdown: 
    wrap: 72
execute: 
  echo: true
knitr:
  opts_chunk: 
    dev: "png"
    dev.args: 
      bg: "transparent"
---

```{r}
#| echo: false
library(tidyverse)
library(here)
```


## Overview

1. The
2. Stuff
3. I'll
4. Talk
5. About

## How to use me

- Most problems can be solved with the 
  [Quarto documentation](https://quarto.org/docs/presentations/).
- Some visual options are built into this template (in addition to those built in to Quarto). In the markdown use square
brackets around text you want to style and the style name in curly brakets. The
extra options are:

## Size 

- `[example text]{.big}`: [example text]{.big}
- `[example text]{.real-big}`: [example text]{.real-big}
    
## Position

- Horizontal centring
- `[example text]{.centre}`

::: fragment
[example text]{.centre}
:::

## Colour

- `[example text]{.blue}`: [example text]{.blue}
- `[example text]{.red}`: [example text]{.red}

## 'Backlight'

- `backlight` produces a light shadow around text.
- Useful for text on top of background images.
- `[example text]{.backlight}`: [example text]{.backlight}
- `[example text]{.inverse-backlight}`: [example text]{.inverse-backlight}

# References

```{r}
#| echo: false
grateful::nocite_references(
  grateful::cite_packages(output = "citekeys", out.dir = here())
)
```


::: refs

:::
